Scientific Reports Title to see here (20 words or less)

### 2016-06-27 draft1.tex
Updated single objective sensitivity to include all patients

\begin{table}[h]
\centering
\scriptsize
\caption{Average Overall State Sensitivity Coefficents For Single Objective Case}
\label{tab:OSSCsoriginalParams}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
Parameter set        & $S_{N}$     & $S_{k_1}$      & $S_{\tau_1}$  & $S_{\tau_2}$   & $S_{\tau_{ach}}$ & $S_{\tau_{nor}}$ & $S_{h_0}$   & $S_{m_{ach}}$ & $S_{m_{nor}}$ \\ \hline
original parameters  & $15.26\pm4$ & $.0792\pm .04$ & $.0739\pm.04$ & $.0156\pm.004$ & $.0540\pm.013$   & $5.5E-4\pm4E-4$ & $19.9\pm 6$ & $.574\pm.7$   & $14.6\pm4$    \\ \hline
estimated parameters & $2.09\pm5$  & $.83\pm3$      & $1.11\pm3$    & $.48\pm2$      & $0.43\pm2$       & $4.18\pm1.6$     & $19.8\pm 6$ & $6.69\pm2$    & $.71\pm 1.6$  \\ \hline
\end{tabular}
\end{table} 
%\begin{table}[]
%\centering
%\caption{Sensitivity by clusters}
%\label{tab:clusterSensitivity}
%\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
%\hline
%Cluster   & $\frac{dh}{dN}$ & $\frac{dh}{k_1}$ & $\frac{dh}{\tau_1}$ & $\frac{dh}{tau_2}$ & $\frac{dh}{\tau_{ach}}$ & $\frac{dh}{\tau_{nor}}$ & $\frac{dh}{h0}$ & $\frac{dh}{m_{nor}}$ & $\frac{dh}{m_{ach}}$ \\ \hline
%Overall   & 4.8352          & 0.2500           & 0.5088              & 0.0033             & 0.0204                  & 0.5720                  & 19.9294         & 1.1339               & 4.4651               \\ \hline
%cluster 1 & 4.7152          & 0.2456           & 0.5027              & 0.0033             & 0.0201                  & 0.5755                  & 19.4780         & 1.1438               & 4.3593               \\ \hline
%cluster 2 & 4.9137          & 0.2528           & 0.5128              & 0.0033             & 0.0206                  & 0.5697                  & 20.2248         & 1.1275               & 4.5344               \\ \hline
%\end{tabular}
%\end{table}
\end{document}

>>>>

\begin{table}[h]
\centering
\scriptsize
\caption{Average Overall State Sensitivity Coefficents For Single Objective Case}
\label{tab:OSSCsoriginalParams}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
Parameter set        & $S_{N}$     & $S_{k_1}$      & $S_{\tau_1}$  & $S_{\tau_2}$   & $S_{\tau_{ach}}$ & $S_{\tau_{nor}}$ & $S_{h_0}$   & $S_{m_{ach}}$ & $S_{m_{nor}}$ \\ \hline
original parameters  & $15.26\pm4$ & $.0792\pm .04$ & $.0739\pm.04$ & $.0156\pm.004$ & $.0540\pm.013$   & $0.00055\pm4E-4$ & $19.9\pm 6$ & $.574\pm.7$   & $14.6\pm4$    \\ \hline
estimated parameters & $2.24\pm5$  & $.89\pm3$      & $1.20\pm4$    & $.61\pm3$      & $0.52\pm2$       & $4.34\pm1.9$     & $20.1\pm 6$ & $6.79\pm2$    & $.83\pm 1.9$  \\ \hline
\end{tabular}
\end{table} 
%\begin{table}[]
%\centering
%\caption{Sensitivity by clusters}
%\label{tab:clusterSensitivity}
%\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
%\hline
%Cluster   & $\frac{dh}{dN}$ & $\frac{dh}{k_1}$ & $\frac{dh}{\tau_1}$ & $\frac{dh}{tau_2}$ & $\frac{dh}{\tau_{ach}}$ & $\frac{dh}{\tau_{nor}}$ & $\frac{dh}{h0}$ & $\frac{dh}{m_{nor}}$ & $\frac{dh}{m_{ach}}$ \\ \hline
%Overall   & 4.8352          & 0.2500           & 0.5088              & 0.0033             & 0.0204                  & 0.5720                  & 19.9294         & 1.1339               & 4.4651               \\ \hline
%cluster 1 & 4.7152          & 0.2456           & 0.5027              & 0.0033             & 0.0201                  & 0.5755                  & 19.4780         & 1.1438               & 4.3593               \\ \hline
%cluster 2 & 4.9137          & 0.2528           & 0.5128              & 0.0033             & 0.0206                  & 0.5697                  & 20.2248         & 1.1275               & 4.5344               \\ \hline
%\end{tabular}
%\end{table}
\end{document}
